### 2023-11-09 manuscript/manuscript.Rmd
clarify sentence about use of correlations

The use of correlations to associate relationships between *m/z* features provides an essential layer of data-driven, internal validation of the mathematically derived solutions.
For instance, if two features that are posited to have the same composition (eg. a C^13^ relationship) but are not significantly correlated within the matrix, it would then be illogical to infer biological assumptions about associations (eg. metabolic pathway changes) of those features with other putatively assigned features within the matrix.

>>>>

The use of correlations to identify relationships between *m/z* features provides an essential layer of data-driven, internal validation of theoretically derived associations.
For instance, if two features that are posited to have the same composition (eg. a C^13^ relationship) but are not significantly correlated within the matrix, it would then be illogical to infer biological assumptions about associations (eg. metabolic pathway changes) of those features with other putatively assigned features within the matrix.
